--- 
title       : Curriculum
subtitle    : 
framework   : revealjs     # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
mode        : selfcontained # {standalone, draft}
revealjs:
  theme: moon
---

```{r preparecode, echo=FALSE, cache=FALSE}
library(ggplot2)
```

# Bram Jans

### Backend Developer

*Looking for a job!*

---
## Education

### [2011–2012] Master of Engineering - Computer Science
<font size="5">
*University of Leuven, Cum Laude*
<br>*Thesis: Creating a database of narrative event chains*
<br>*Specialization Software Engineering and Artificial Intelligence*
<br>*5 months exchange at the Autonomous University of Barcelona, Spain*
</font>

### [2006–2009] Bachelor of Informatics
<font size="5">*University of Leuven*</font>

---
## Jobs

### [2013-Now] Backend developer, DataCamp
<font size="5">
Worked on various web dev projects:
<br>The [DataCamp.com](https://www.datacamp.com) backend, a RESTful API in Ruby on Rails
<br>Rdocumentation.org, another Rails app communicating with a backend server running R
</font>

### [2011–2012] IT Consultant, Altran Belgium
<font size="5">
Worked full-time with client Elia, owner of the Belgian electricity network. Creation of a new technical and business specifications document, working with Microsoft SQL Server and testing applications provided by a 3rd party company.
</font>

#### [2010–2011] Student job: Data mining, Brains and Business
<font size="5">Development of a business analysis tool written in REALbasic.</font>

---
## Skills

```{r skills-plot, results='asis', echo = FALSE, cache = FALSE}
df = data.frame(c("Ruby (on Rails)", "HTML/CSS", "SQL", "R", "Linux", "Javascript"), c(8, 6, 7, 6, 7, 5))
colnames(df) = c("language", "score")
d = ggplot(data=df, aes(x=language, y = score))
d = d + geom_bar(position="dodge",stat="identity") + coord_flip() 
d = d + scale_y_continuous(breaks = seq(0, 12, 1)) 
d = d + theme(axis.text.x = element_text(size=24, family="Helvetica"),axis.text.y = element_text(size=24))
d
```

#### And notions of

<font size="5">Java, Python, Node.js, Matlab, REALbasic</font>

---
## Languages

- Dutch (native)
- English (advanced)
- Spanish (advanced)
- French (intermediate)

